Human Factors Influencing Visual Statistical Inference

### 2013-06-05 sociology_paper.tex
appendix for lineup results

>>>>

\clearpage
\section{Electoral Building Lineups and Results}
Figures~\ref{fig:elect.1} through~\ref{fig:elect.5} show the five lineups shown to (different) Amazon Turk workers in an experiment. They all are created as described in the introduction of the paper. In order to not bias observers, no context information was given about how these plots were created or what data they were displaying. This also made it necessary to slightly more stylize the display.

% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Wed Jun  5 17:39:09 2013
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 lineup & \#1 & \#2 & \#3 & \#4 & \#5 \\ 
  \hline
  \# correct/ \#evaluation &  12/72 & 11/66 & 5/74 & 14/72 & 19/57 \\ 
$p$-value & 0.00023 & 0.00041 & 0.31 & 1.2e-05 &  1.9e-11 \\ 
data panel & $3\cdot4+1$ & $2^4+1$ & $4^2+2 $ & $12+\sqrt{25}$ & $2^3-7$ \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Wed Jun  5 18:00:55 2013
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrrrrrrrrrrrrrr}
  \hline
& \multicolumn{10}{l}{panel chosen}\\
Lineup & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 \\ 
  \hline
\#  1 & 2 & 2 & 0 & 10 & 2 & 2 & 6 &  23 & 1 & 1 & 0 & 1 & \bf 12 & 3 & 3 & 1 & 0 & 1 & 1 & 1 \\ 
\#  2 & 0 & 16 & 1 & 1 & 5 & 1 & 0 & 8 & 0 & 2 & 0 & 0 & 0 & 4 & 2 & 1 & \bf 11 & 1 & 0 & 13 \\ 
\#  3 & 7 & 26 & 0 & 2 & 0 & 5 & 3 & 0 & 2 & 1 & 0 & 4 & 0 & 0 & 2 & 0 & 9 & \bf 5 & 0 & 6 \\ 
\#  4 & 0 & 0 & 0 & 2 & 0 & 0 & 0 & 3 & 1 & 10 & 2 & 18 & 1 & 0 & 4 & 2 &\bf 14 & 0 & 13 & 0 \\ 
\# 5 &\bf 19 & 1 & 4 & 1 & 0 & 1 & 0 & 12 & 0 & 0 & 0 & 4 & 1 & 0 & 0 & 12 & 1 & 1 & 0 & 0 \\ 
   \hline
\end{tabular}
\caption{\label{tab:response}Overview of all choices by observers for each of the lineups. The correct choice is bolded. In most lineups there are null plots that were picked more often by observers, but the actual result is among the plots being picked most often, indicating that there is some indication that the election result is not completely consistent with the polls.}
\end{table}

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=0.8\linewidth]{electoral-5-13.pdf} 
   \caption{Lineup \#1 - electoral building. Which building looks the most different from the other buildings? }
   \label{fig:elect.1}
\end{figure}

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=0.8\linewidth]{electoral-2-17.pdf} 
   \caption{Lineup \#2 - electoral building. Which building looks the most different from the other buildings? }
   \label{fig:elect.2}
\end{figure}
\begin{figure}[htbp] 
   \centering
   \includegraphics[width=0.8\linewidth]{electoral-3-18.pdf} 
   \caption{Lineup \#3 - electoral building. Which building looks the most different from the other buildings? }
   \label{fig:elect.3}
\end{figure}
\begin{figure}[htbp] 
   \centering
   \includegraphics[width=0.8\linewidth]{electoral-4-17.pdf} 
   \caption{Lineup \#4 - electoral building. Which building looks the most different from the other buildings? }
   \label{fig:elect.4}
\end{figure}
\begin{figure}[htbp] 
   \centering
   \includegraphics[width=0.8\linewidth]{electoral-1-1.pdf} 
   \caption{Lineup \#5 - electoral building. Which building looks the most different from the other buildings? }
   \label{fig:elect.5}
\end{figure}
